How did the introduction of Stemmed Points affect Mobility and Site Occupation during the Late Pleistocene in Korea?

### 2020-12-05 analysis/paper/paper.Rmd
still not perfect image 1 but arrangement is good

@@

```{r korea_map, fig.cap="Site map. Korean Paleolithic sites mentioned in the text."}
source(here::here("analysis/paper/001-draw-the-map.R"))
knitr::include_graphics(here::here("analysis/figures/001-site-map.png"))
```

>>>>

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  dpi = 300,
  fig.path = "../figures/"
)
```

<!---```{r}
quietly <- function(x) {
  sink(tempfile())
  on.exit(sink())
  invisible(force(suppressMessages(x)))
}

``` --->

@@

```{r korea_map, fig.cap="Site map. Korean Paleolithic sites mentioned in the text."}
source(here::here("analysis/paper/001-draw-the-map.R"))
knitr::include_graphics(here::here("analysis/figures/001-site-map.png"))

```
